\assignment{1}{The Kinematic Model}{Due Thursday, April 8 at 5:00pm PDT}{Chris Gerdes, 2017}

\hspace{0.5cm}

\section*{Purpose}

There is a lot we can learn about the design and control of vehicles using simple models. To start off, we have a few exercises to familiarize yourself with the notation of coordinate transformations and rotation matrices introduced on the first day of class and to gain some more insight into the kinematic model. You will also build a simple simulation and test controllers capable of tracking a path with the kinematic model.



\section*{Instructions}

This and following homework assignments will be submitted using two different tools, \GSno{} and \GRno{}.
Throughout the assignment, each prompt will be marked with either \GS{} or \GR{} to make it clear
where you should be submitting the answer to that problem. \GRno{} questions will also be shown in
\textbf{\color{blue}Blue} to make them easy to see.

All written portions must be turned in through Gradescope. We will provide three different homework formats on Canvas (a latex template, a pdf template, and a condensed pdf template). Whatever format you decide to use, please \fbox{\textbf{BOX}} all of your final answers.

Some problems will make use of the \GRno{} suite discussed in class. These problems are available directly from Canvas
by clicking on each individual question.
You are allowed to submit code to \GRno{} as many times as you want before the due date without penalty. In this
way you can be sure each function or script passes all of the assessments that go along with it before moving on to the
next problem. We encourage you to write
your own test cases as well to ensure your code is working as expected. 


\newpage
