\assignment{7}{Navigating the Hairpin Corner}{Due Thursday, June 3rd at 5:00pm PST}{Chris Gerdes, 2017}
\hspace{0.5cm}

\section*{Purpose}

In this assignment, we will add longitudinal and lateral weight transfer to our bicycle model and see how handling at
the limits of tire friction can be influenced by load transfer.  
We'll consider load transfer caused by braking, acceleration, and suspension roll stiffness.  

We'll explore these concepts while using a new tire model, the Pacejka Magic Formula (MF). The MF tire model is a semi-empirical model that has stood as a reference point in tire modelling since its introduction in the late 1980s. 

Download the source code zip folder \verb!hw7.zip! from Canvas. In it you'll find the code you'll need for
Problems 1, 3 and 4.

\section*{Instructions}

This and following homework assignments will be submitted using two different tools, \GSno{} and \GRno{}.
Throughout the assignment, each prompt will be marked with either \GS{} or \GR{} to make it clear
where you should be submitting the answer to that problem. \GRno{} questions will also be shown in
\textbf{\color{blue}Blue} to make them easy to see.

All written portions must be turned in through Gradescope. See the Piazza post on homework guidelines for more
instructions on the different homework resources available to you. Whatever format you decide to use, please \fbox{\textbf{BOX}} all of your final answers.

Some problems will make use of the \GRno{} suite discussed in class. These problems are available directly from Canvas
by clicking on each individual question.
You are allowed to submit code to \GRno{} as many times as you want before the due date without penalty. In this
way you can be sure each function or script passes all of the assesments that go along with it before moving on to the
next problem. We encourage you to write
your own test cases as well to ensure your code is working as expected. 

Additionally, some problems will make use of \textbf{MATLAB Online} or a normal MATLAB desktop installation. For these
problems we will give you most of the source code needed for the problem. See our Piazza post for more information 
about how to setup MATLAB Online.

When writing functions and running simulations, use the set of parameters given to you for Niki. These will be available
in each \GRno{} problem where they are appropriate. 
The values of these paramters for Niki are also given in Appendix \ref{appendix:Vehicle Parameters} and
\ref{appendix:Tire Parameters} at the end of this document.


\newpage
