\assignment{3}{Transient Response Characteristics}{Due Thursday, April 22 at 5pm}{Chris Gerdes, 2021}

\hspace{0.5cm}

\section*{Purpose}

This past week in class we looked at the transient response characteristics of the bicycle model with linear
tires. The conclusions reached from this simple model can be extrapolated to many more complicated vehicle
dynamics problems so it makes sense to get some familiarity with the model and, in particular, what it means
for pole locations and response characteristics.


\section*{Instructions}

This and following homework assignments will be submitted using two different tools, \GSno{} and \GRno{}.
Throughout the assignment, each prompt will be marked with either \GS{} or \GR{} to make it clear
where you should be submitting the answer to that problem. \GRno{} questions will also be shown in
\textbf{\color{blue}Blue} to make them easy to see.

All written portions must be turned in through Gradescope. See the Piazza post on homework guidelines for more
instructions on the different homework resources available to you. Whatever format you decide to use, please \fbox{\textbf{BOX}} all of your final answers.

Some problems will make use of the \GRno{} suite discussed in class. These problems are available directly from Canvas
by clicking on each individual question.
You are allowed to submit code to \GRno{} as many times as you want before the due date without penalty. In this
way you can be sure each function or script passes all of the assesments that go along with it before moving on to the
next problem. We encourage you to write
your own test cases as well to ensure your code is working as expected.

\newpage
