\secApp{MATLAB}


\subsection*{MATLAB Background}

MATLAB is widely used in the automotive industry and in engineering more generally.  As a result of its broad application, MATHWORKS has developed various toolboxes for industry-specific needs.  Given this, it's often not necessary to download all toolboxes that MATHWORKS offers and companies will usually purchase only the toolboxes that are needed by their engineers.  

\subsection*{MATLAB Installation}
To install MATLAB and any associated toolboxes, go to the MATHWORKS website (\url{www.mathworks.com}) and create an account using your Stanford email. This will give you access to the complete version of MATLAB. Follow the instructions on the MATHWORKS website to download the software.


\subsection*{MATLAB Version}
Mathworks tries to give both backward and forward compatibility to MATLAB.  This is not always true and is especially tricky with certain toolboxes.  Downloading the latest version of MATLAB (2021a) should work for everything we're doing in this class.  If you already have an older version of MATLAB installed on your computer, don't worry about upgrading to the latest version.  Should any compatibility issues arise, the teaching team will handle them with you on a case-by-case basis.

\subsection*{MATLAB Toolboxes}
We require downloading these toolboxes in order to use the framework we have developed for the project:
\\MATLAB 2021a
\\Control System Toolbox
\\DSP System Toolbox

Simulink and Stateflow will not be used in this class, but they are widely used in research and industry.  You may find it helpful to download these now for future use.  You can always return later to download additional toolboxes.
